### 2024-03-26 README.Rmd
infer 1.0.7 release candidate (#536)
* update redirecting URL

* update CRAN comments

* Increment version number to 1.0.7

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on Posit Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues). Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).

>>>>

For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on Posit Community](https://forum.posit.co/new-topic?category_id=15&tags=tidymodels,question). If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/infer/issues). Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code. Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).
